\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-13 article.tex
abc

The instruction set used in this paper will be a union of the sets used in the 2022 and 2023 compilers courses in order to work as a drop-in replacement of LLVM for either of the two respective source languages:  Tiger and Dolphin. This instruction set is a subset of the one used in practice, as, for instance, neither of the languages implemented support interrupts, floating point operations and so on, and instead only strive to cover the basics of compilers.

Some additional instructions are included, like \lstinline!trunc! and \lstinline!switch!, to widen the range of supported frontend languages with the clang compiler.
%been added in order to help cover more generated LLVM. % FIXME
%with only four distinct block terminators 
%\begin{enumerate}
%    \item Unconditional \lstinline!br! followed by the label to branch to
%    \item Conditional \lstinline!br!  followed by an \lstinline!i1! condition and two labels
%    \item \lstinline!ret! followed by an optional return value
%    \item \lstinline!unreachable!
%\end{enumerate}
%The branching for most of these is trivial: after successful execution the flow of all but \lstinline!br!, \lstinline!ret! and \lstinline!unreachable! will unconditionally attempt to execute the next instruction in memory (i.e. increment the instruction pointer by instruction length).

>>>>

The instruction set used in this paper will be a union of the sets used in the 2022 and 2023 compilers courses in order to work as a drop-in replacement of LLVM for either of the two respective source languages:  Tiger and Dolphin. This instruction set is a subset of the one used in practice, as, for instance, neither of the languages implemented support interrupts, floating point operations etc., and instead only strive to cover the basics of compilers. In additional some other instructions are also included, like \lstinline!trunc! and \lstinline!switch!, to widen the range of supported frontend languages with the clang compiler.
%been added in order to help cover more generated LLVM. % FIXME
%with only four distinct block terminators 
%\begin{enumerate}
%    \item Unconditional \lstinline!br! followed by the label to branch to
%    \item Conditional \lstinline!br!  followed by an \lstinline!i1! condition and two labels
%    \item \lstinline!ret! followed by an optional return value
%    \item \lstinline!unreachable!
%\end{enumerate}
%The branching for most of these is trivial: after successful execution the flow of all but \lstinline!br!, \lstinline!ret! and \lstinline!unreachable! will unconditionally attempt to execute the next instruction in memory (i.e. increment the instruction pointer by instruction length).
